Fréchet Distance

### 2022-11-05 docs/paper.tex
removed old scrpage2
docs: bump
wip: introduction chapter

%%%
%%% layout
%%%

%%% scrpage2: KOMA heading and footer
%%% Note: if you don't use this package, please remove 
%%%       \pagestyle{scrheadings} and corresponding settings
%%%       below too.
\usepackage[automark]{scrpage2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% set heading and footer
%%%

%%% scrheadings default: 
%%%      footer - middle: page number
\pagestyle{scrheadings}

%%% user specific
%%% usage:
%%% \position[heading/footer for the titlepage]{heading/footer for the rest of the document}

%%% heading - left
% \ihead[]{}

%%% heading - center
% \chead[]{}

%%% heading - right
% \ohead[]{}

%%% footer - left
% \ifoot[]{}

%%% footer - center
% \cfoot[]{}

%%% footer - right
% \ofoot[]{}

@@

\section{Intro}
\subsection{Conventions}
Some Text \cite{DBLP:journals/ijcga/AltG95}

>>>>

@@

@@

\section*{Abstract}

\section{Introduction}
% motivation

% two (polygonal) curves

% Hausdorff distance
The commonly known \textit{Hausdorff distance} can be understood 
as the largest distance between any two points on the curves 
and is calculated by \autoref{eq_hausdorff_distance} \cite{alt_computing_1995}.

\begin{align}
  \label{eq_hausdorff_distance}
  \delta_{hd}(P,Q) = \max \left( \sup_{p \in P} \inf_{q \in Q} \text{dist}(p,q), \sup_{q \in Q} \inf_{p \in P} \text{dist}(p,q) \right)
\end{align}

However, this metric does not take the course of the curves into account. 
Two curves may be very dissimilar in the preception of a human 
but still have a small Hausdorff-distance, see \autoref{fig_hausdorff_distance_bad_example}.

\begin{figure}[ht]
  % TODO: insert figure
  \caption[Hausdorff distance of two dissimilar curves]{The two shown curves are dissimilar (in a common sense) depsite having a small Hausdorff distance.}
  \label{fig_hausdorff_distance_bad_example}
\end{figure}

% Fréchet distance motivation

% continuous Fréchet distance equation

% Scope

% Fréchet distance Variants 
\section{Variants}
Through the years many slightly differnt variants of the continuous Fréchet distance have evolved. 
The continuous Fréchet distance takes into account every single point on the curves, 
with interpolation in the case of polygonal curves, 
without allowing to walk backwards 
and without any obstacles in between the two curves.

% TODO: Why allow it? Better algorithms?
The \textit{weak Fréchet distance} slightly modified the continuous version by allowing 
going backwards.

% TODO: Is that mapping bijective? Add sources
The \textit{discrete Fréchet distance} 
This gives an upper bound on the continuous Fréchet distance % Source?
and is often used as a approximation. % Source?
% discrete Fréchet distance and contrast to hausdorff distance

% (Geodesic Fréchet distance)

% (Homotopic Fréchet distance)

\section{Algorithm}
% Original algorithm for the continuous Fréchet distance

% Free Space Diagram

% Runtime analysis (?)
% Correctness proof (?)

\section{Conclusion}
